\section{Speculative Attack Replication}

To our knowledge, speculative attacks have not been implemented on BOOM yet. Thus,
one of the focuses of this project was to demonstrate simple proof of concepts for a
subset of speculative style attacks. Originally, the goal was to implement both 
Spectre-v1, otherwise know as the Bounds Check Bypass attack, and the Return Stack Buffer attack \cite{b3}.
However, due to the instability of BOOM that was being used, the team instead implemented
proof of concepts for Bounds Check Bypass attack and Spectre-v2, which is otherwise known as the
Branch Target Injection attack. The open-source code is available at https://github.com/riscv-boom/boom-attacks.

\subsection{Implementation Details}

This project utilizes the Berkeley Out-of-Order Machine (BOOM), a synthesizable and 
parameterizable open source RV64G RISC-V core written in the Chisel hardware construction language \cite{b49}. 
The microarchitecture is open source, providing the team insight into the front-end and memory system
used. This insight allowed the team to quickly replicate the attacks and determine the relevant parameters
for the attacks to be efficient. Despite this efficiency using BOOM and the RISC-V ecosystem, a few issues
had to be addressed to successfully replicate the attacks.

\subsubsection{Flushing a cache line}

% TODO: what is the arm instruction for clflush
% TODO: put in probability of evicting a relevant line?

One feature of many x86 and ARM ISAs is the availability of a cache manipulation instructions
(for example x86 has {\tt clflush} to flush a cache line from every level of the cache hierarchy).
However, the RV64G ISA that BOOM runs does not have a corresponding {\tt clflush} equivalent.
This type of instruction is extremely important for the cache side channel attacks that the team is
replicating since it allows for timing leaks depending on if the cache line is
present in the cache hierarchy. Therefore, a workaround was made to implement an equivalent
L1 cache line flush function. This function takes in an address and size in bytes, and flushes
all sets starting from that address until the size. This is done by having an extra array which 
is a multiple of the L1 cache size, that when indexed into, evicts a cache line within the set that the input
address refers to. While {\tt clflush} is able to selectively remove a cache line from the cache without 
affecting the rest of the cache state, this function created instead is only able to evict the entire set.
This enforces that the cache line referenced is evicted at the cost of evicting other lines, causing a performance
decrease. Evicting the entire set is done by accessing the extra array addresses corresponding to the set an 
{\tt N * L1\_WAY} amount, where {\tt N} is large enough to account for the random cache replacement policy. The larger
the {\tt N} value, the higher chance that the particular cache line is evicted from the set. For our purposes, this value
was chosen to be {\tt N = 4} in order to have a high probablility of evicting the referenced cache line.

\subsubsection{BOOM Branch Predictor Unit}

% TODO: double check that the ghr is hashed and folded

The BOOM Branch Predictor Unit (BPU), is split into a single-cycle "next-line predictor" (NLP) and a
slower but more complicated "backing predictor" (BP). The NLP contains the Branch Target Buffer (BTB) 
where more recent branches are cached alongside their target, a tag of the PC, and more metadata. Additionally,
the NLP contains the Return Stack Buffer (RSB) which holds the return pointer for a {\tt ret} instruction. The BP
consists of a large predictor such as a TAGE or GShare predictor which makes a more accurate prediction based on
a larger view of the branch history \cite{b47}. For simplicity, the team decided to use a GShare predictor, since it is 
easier to train and was fully functioning at the start of the project (the TAGE BP had multiple performance bugs
associated with it). The GShare predictor used had a global history of 23 bits and history table containing
4096 counters. Since the global history was longer than the size of the table, the global history was hashed with
the instruction PC and folded to index into the history table. Additionally, when trying to
implement the RSB attack, it was discovered that the RSB was disabled resulting in all {\tt ret} instructions
to speculate to the next PC instead of the return target PC. Re-enabling the RSB lead to multiple other BPU bugs,
so the team decided to keep the RSB disabled and instead implement the Branch Target Injection attack which did not
use the RSB.

\subsubsection{BOOM Memory System}

% TODO: does this make sense to people

BOOM's memory system utilizes the RocketChip L1 Data Cache and connects to the rest of the RocketChip
uncore. However, in the configuration of BOOM used, there is a L1 cache and outer memory set to a L2 cache
latency. This memory hierarchy still functions properly, however it was noticed that the speculation window
was not large enough due to memory latencies not being sufficiently large. This is because the
dependent load causing speculation would resolve quickly, resulting in other speculative loads to be reached.
Thus, a workaround was made to use BOOM's floating point unit to expand the speculation 
window using {\tt fdiv} instructions. When used on the dependency, this would allow the speculation
to run for a longer time allowing the speculative loads used for the attack to issue.

\subsection{Bounds Check Bypass Attack}

This attack exploits the functionality of conditional branches to leak a secret byte 
when and attacker resides in the same address space. The attack works by a 
malicious entity training a conditional branch within victim code to predict the branch
to be taken in a certain direction, then during the attack round, the malicious entity
gives a value to the victim that fails the bounds check in the victim but during
speculation is used to retrieve the secret value. This particular attack variant
uses a cache side channel attack to leak the information by having a passed in value retrieve
a secret value which is then used to index "attacker array". After the attack is run, this 
"attacker array" can be scanned and timed to determine the secret value based on if there
is a cache hit. The psuedocode for this type of attack in \ref{code:spectre-v1-pseudo}
demonstrates the basic principle of the attack using a C-like syntax.

\begin{lstlisting}[style=column-code, caption=Psuedocode of Bounds Check Bypass Attack]
char* secret[] = "SECRET_VALUE"
char  attackArray[256 * CACHE_BLOCK_SZ]

void victim(idx){
  if (idx < secret.size()){
    attackArray[secret[idx] * CACHE_BLOCK_SZ]
  }
}

int main(void){
  
  // Training
  while (TRAINING_ROUNDS){
    victim(idx)
  }

  // Attack. Read secret value
  victim(outOfBoundsIdx)

  // Probe array to check for hit
  for (i -> 0 until 256){
    t0 = time()
    attackArray[i * CACHE_BLOCK_SZ]
    t1 = time()
  }
}
\end{lstlisting}\label{code:spectre-v1-pseudo}

% TODO: double check the bpu hashing

The BOOM implementation of this attack echos the Spectre-v1 PoC and the psuedocode closely.
It consists of three different parts. First, a tally buffer is cleared before reading a secret byte.
This tally buffer is used to keep track of the amount of hits a secret value gets during the measurement
phase. Next the array to be probed is evicted from the cache (the "attacker array" mentioned above), and
the attack trains the BPU to enter the bounds protected area within the victim function. Note that in
this section, there is an extra loop that puts the branch history in a consistent state since the branch
history is hashed on update. Finally, the attacker code reads out the probing array through using the
{\tt rdcycle} instruction and checking if the result is under a hand tuned cache threshold. Full code for 
this attack is visible below at \ref{code:boom-spectre-v1}.

\subsection{Branch Target Injection Attack}

This attack exploits the functionality of the BTB in predicting the outcome
of {\tt jalr} instructions that use the BTB to predict where it will branch. Specifically, 
the attack works by a malicious entity training a BTB entry for a {\tt jalr} instruction to point to 
the victim code. Then during the attack run, when the {\tt jalr} is supposed to go to another function,
the BTB redirects the PC to the victim code where it speculatively leaks the secret value. Similar to the
Bounds Check Bypass attack, this attack leaks information through the
cache side channel mentioned in \ref{ref:Bounds Check Bypass Attack}. The psuedocode in 
\ref{code:spectre-v2-psuedo} demonstrates the basic principle of the attack using a C-like syntax.

\begin{lstlisting}[style=column-code, caption=Psuedocode of Bounds Check Bypass Attack]
char* secret[] = "SECRET_VALUE"
char  attackArray[256 * CACHE_BLOCK_SZ]

void otherFunction(void){
  // Other functionality    
}

void victim(idx){ attackArray[secret[idx] * CACHE_BLOCK_SZ] }

int main(void){
  
  // Training
  while (TRAINING_ROUNDS){
    jump(victim)
  }

  // Attack. Read secret value
  argument = attackIdx
  jump(otherFunction)

  // Probe array to check for hit
  for (i -> 0 until 256){
    t0 = time()
    attackArray[i * CACHE_BLOCK_SZ]
    t1 = time()
  }
}
\end{lstlisting}\label{code:spectre-v2-pseudo}

The BOOM implementation of this attack is very similar to the implementation given for
the Bounds Check Bypass attack listed in \ref{ref:Bounds Check Bypass Attack}. One of the main differences
for this attack is that the attacker has to change both the address of the function being called through
{\tt jalr} and the pass in value to the victim function throughout the training and the attack run.
Another difference between the two attacks is that the {\tt fdiv} manipulation is instead done on the target address
in the main function instead of using {\tt fdiv} on the passed in index in the victim code.
